\tool: Revisiting BadUSB with Type-C

### 2021-01-30 WOOT/Files/experiment.tex
fully2full

To test the capability of the fully control mode, we chose iPad Pro (3rd
	generation), a tablet in iOS 14.3 with a USB Type-C interface, as the target
device in this experiment.  Besides disguising as normal HID devices like a
conventional BadUSB~\cite{badusb}, \tool also transmitted real-time video
stream from the target device to the attacker via WiFi.  After the connection
establishment, the attacker performed a series of actions to test the capability of
\tool. In the beginning, the attacker accessed the album application on the iPad and
obtained all the photos inside. After that, the attacker sent messages via victim's
account. At last, the attacker performed a transaction using the
financial application. All of these tests resulted in success.

@@

Next, we summarize the possible threats toward user under different modes.
\hongyi{Better way to express this?}
First, under HID emulator mode, the attacker is able to implant malware and backdoor script into victims' devices. Moreover, using video capture mode, once the victims access their sensitive data like QR payment  code or album, their sensitive data will be immediately transmitted via \tool to the attacker. Lastly, with fully control mode, the attacker has complete control over the victims' device and can conduct any action on the victim device.

\shuqing{Background is longer than real user study.}
%As the functionality and effectiveness, HID emulator mode is similar to the original BadUSB and the fully control mode hijacks the victim's device completely.
\hongyi{I dont know if it's a good enough reason}
%Here we only validate the usability of privacy extraction mode and conducted a user study.

>>>>

To test the capability of the full control mode, we chose iPad Pro (3rd
	generation), a tablet in iOS 14.3 with a USB Type-C interface, as the target
device in this experiment.  Besides disguising as normal HID devices like a
conventional BadUSB~\cite{badusb}, \tool also transmitted real-time video
stream from the target device to the attacker via WiFi.  After the connection
establishment, the attacker performed a series of actions to test the capability of
\tool. In the beginning, the attacker accessed the album application on the iPad and
obtained all the photos inside. After that, the attacker sent messages via victim's
account. At last, the attacker performed a transaction using the
financial application. All of these tests resulted in success.

@@

Next, we summarize the possible threats toward user under different modes.
\hongyi{Better way to express this?}
First, under HID emulator mode, the attacker is able to implant malware and backdoor script into victims' devices. Moreover, using video capture mode, once the victims access their sensitive data like QR payment  code or album, their sensitive data will be immediately transmitted via \tool to the attacker. Lastly, with full control mode, the attacker has complete control over the victims' device and can conduct any action on the victim device.

\shuqing{Background is longer than real user study.}
%As the functionality and effectiveness, HID emulator mode is similar to the original BadUSB and the full control mode hijacks the victim's device completely.
\hongyi{I dont know if it's a good enough reason}
%Here we only validate the usability of privacy extraction mode and conducted a user study.
